Per captia consumption

### 2021-06-15 PerCapitaConsumption.Rmd
add consumption tables for NOBA and CCA

```{r, eval=FALSE}

@@

source(here("config/omdimensions.R"))

@@

@@

>>>>

```{r}

@@

source(here("config/omdimensions.R"))
source(usersurvey[2])

@@

For example, NOBA cod daily per capita intake is tens of grams for older age classes, but is 3-4x lower than expected:

```{r}
DT::datatable(as.data.frame(survey_totcons%>%filter(species=="North_atl_cod")),
              rownames = FALSE,
              options = list(pageLength = 25, 
                         order = list(list(0, 'asc')))
)
```

@@

For example, CCA arrowtooth flounder should have a daily per capita intake in at least tens of grams for older age classes:

```{r}
knitr::kable(as.data.frame(survey_totcons%>%filter(species=="Arrowtooth_flounder")))
```
